### 2021-04-28 treatise-context/4_simulation.tex
pdflatex: Shrink figure width

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m{\M {P} \in \MB {C} ^{N_B^2 \D N_{H,t} N_{H,r}}}, \m{\V {y} \in \MB {C} ^{N_B ^2}}, \m {\g_{\Rm {DS}} > 0}.
%
\item Define \m {\T {\V {y}}, \T {\V {g}}, \T {\M {P}}, \T {\M {P}} ^\Adj, \T {\V {z}}}, according to \Rf {y:y:Ry:Ny}.
%
\item Compute the convex program
\DispNum {g:f:gf:S1} {
\NC \Hat {\T {\V {g}}}, \Hat {\T {\V {f}}}
\LA \NC \startcases
   \NC \Min {\T {\V {g}}', \T {\V {f}}'}  \MC \IP {\V {1}, \T {\V {f}}'} \NR
   \NC \Rm {subject} \; \Rm {to} \MC \T {\V {g}}' \preceq \T {\V {f}}' \NR
   \NC \MC - \T {\V {g}}' \preceq \T {\V {f}}' \NR
   \NC \MC \T {\M {P}}^\Adj \T {\M {P}} \T {\V {g}}' \preceq \T {\M {P}}^\Adj \T {\V {y}} + \g_{\Ss {DS}} \V {1} \NR
   \NC \MC - \T {\M {P}}^\Adj \T {\M {P}} \T {\V {g}}' \preceq - \T {\M {P}}^\Adj \T {\V {y}} + \g_{\Ss {DS}} \V {1} \NR
\stopcases \NR
}
\item Convert
%
\DispNum {g:::R1:1g} {
\NC \Hat{\V {g}}
\LA \NC \MS {R} ^{-1} \SB {\Hat{\T{\V {g}}}} \NR
}
\item Calculate
%
\DispNum {G:G:ve:1g} {
\NC \Hat {G}
\LA \NC \Rm {vec}^{-1} \SB {\Hat {g}} \NR
}
\item Calculate
%
\DispNum {H:H:KG:GK} {
\NC \Hat {\M {H}}
\LA \NC \M {K} \Hat {\M {G}} \M {K}^\Adj \NR
}
\item Output \m {\Hat {\M {H}}}.
\stopitemize
}

@@

For Lasso, \m {\l _{\Rm {Lasso}}} is also crucial to the performance, but cannot be obtained in advance.
Thus, for sake of comparison, we set the same threshold for Lasso and DS.
In view of the fact that \m {\VNm {g} _1 \leq 2 N_{H,t} N_{H,r} \VNm {g} _\infty}, we tentatively set \m {\l _{\Rm {DS}} =  2 N_{H,t} N_{H,r} / \g _{\Rm {DS}}} and \m {\l _{\Rm {Lasso}} =  1 / \g _{\Rm {Lasso}}}.
Still, there may be other values of \m {\g} (or \m {\l}) for which DS and Lasso are both better.

@@

In the following, we plot for different values and ratios of \m {N_B, N_{H,t}, N_{H,r}}.
We fix \m {N_R = \RB {3/2} N_B}.
%
\blank [big]
\externalfigure [error-medium-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [error-medium-more-wide-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [error-medium-more-tall-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [error-small-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [error-small-more-wide-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 2, N_{H,t} = 8, N_{H,r} = 6}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [error-small-more-tall-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 8}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [error-big-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 18}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [error-big-more-wide-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 6, N_{H,t} = 24, N_{H,r} = 18}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [error-big-more-tall-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 24}, with \m {6} stages, error.}

@@

In the following, we plot for \m {N_Y = N_R}, for different ratios of \m {N_{H,t}, N_{H,r}}.
%
\blank [big]
\externalfigure [error-medium-equal-square-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_R = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [error-medium-equal-tall-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_R = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [error-medium-equal-wide-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_R = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}

@@

In the following, we plot for \m {N_B = 4}, for different number of stages.
%
\blank [big]
\externalfigure [error-medium-more-square-three-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {3} stages, error.}
%
\blank [big]
\externalfigure [error-medium-more-wide-three-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {3} stages, error.}
%
\blank [big]
\externalfigure [error-medium-more-tall-three-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {3} stages, error.}
%
\blank [big]
\externalfigure [error-medium-more-square-nine-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {9} stages, error.}
%
\blank [big]
\externalfigure [error-medium-more-wide-nine-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {9} stages, error.}
%
\blank [big]
\externalfigure [error-medium-more-tall-three-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {9} stages, error.}

@@

In the following, we plot for different thresholds, for \m {N_B = 4}, focusing on each of OMP, Lasso, DS.
%
\blank [big]
\externalfigure [error-medium-more-square-six-oommpp.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
%
\blank [big]
\externalfigure [error-medium-more-wide-six-oommpp.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
%
\blank [big]
\externalfigure [error-medium-more-tall-six-oommpp.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of OMP, error.}
%
\blank [big]
\externalfigure [error-medium-more-square-six-lasso.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
%
\blank [big]
\externalfigure [error-medium-more-wide-six-lasso.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
%
\blank [big]
\externalfigure [error-medium-more-tall-six-lasso.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of Lasso, error.}
%
\blank [big]
\externalfigure [error-medium-more-square-six-ddss.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
%
\blank [big]
\externalfigure [error-medium-more-wide-six-ddss.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
%
\blank [big]
\externalfigure [error-medium-more-tall-six-ddss.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of DS, error.}

@@

When plotting runtime statistics, we only consider the cases where \m {N_{H,t} = N_{H,r} = 3 N_B}.
%
\blank [big]
\externalfigure [time-medium-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [time-small-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [time-big-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 18}, with \m {6} stages, error.}

>>>>

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m{\M {P} \in \MB {C} ^{N_B^2 \D N_{H,t} N_{H,r}}}, \m{\V {y} \in \MB {C} ^{N_B ^2}}, \m {\g_{\Rm {DS}} > 0}.
%
\item Define \m {\T {\V {y}}, \T {\V {g}}, \T {\M {P}}, \T {\M {P}} ^\Adj, \T {\V {z}}}, according to \Rf {y:y:Ry:Ny}.
%
\item Compute the convex program
\DispNum {g:f:gf:S1} {
\NC \Hat {\T {\V {g}}}, \Hat {\T {\V {f}}}
\LA \NC \startcases
   \NC \Min {\T {\V {g}}', \T {\V {f}}'}  \MC \IP {\V {1}, \T {\V {f}}'} \NR
   \NC \Rm {subject} \; \Rm {to} \MC \T {\V {g}}' \preceq \T {\V {f}}' \NR
   \NC \MC - \T {\V {g}}' \preceq \T {\V {f}}' \NR
   \NC \MC \T {\M {P}}^\Adj \T {\M {P}} \T {\V {g}}' \preceq \T {\M {P}}^\Adj \T {\V {y}} + \g_{\Ss {DS}} \V {1} \NR
   \NC \MC - \T {\M {P}}^\Adj \T {\M {P}} \T {\V {g}}' \preceq - \T {\M {P}}^\Adj \T {\V {y}} + \g_{\Ss {DS}} \V {1} \NR
\stopcases \NR
}
\item Convert
%
\DispNum {g:::R1:1g} {
\NC \Hat{\V {g}}
\LA \NC \MS {R} ^{-1} \SB {\Hat{\T{\V {g}}}} \NR
}
\item Calculate
%
\DispNum {G:G:ve:1g} {
\NC \Hat {G}
\LA \NC \Rm {vec}^{-1} \SB {\Hat {g}} \NR
}
\item Calculate
%
\DispNum {H:H:KG:GK} {
\NC \Hat {\M {H}}
\LA \NC \M {K} _r \Hat {\M {G}} \M {K}^\Adj _t \NR
}
\item Output \m {\Hat {\M {H}}}.
\stopitemize
}

@@

For Lasso, \m {\l _{\Rm {Lasso}}} is also crucial to the performance, but cannot be obtained in advance.
Thus, for sake of comparison, we set the same threshold for Lasso and DS.
In view of the fact that \m {\VNm {g} _1 \leq 2 N_{H,t} N_{H,r} \VNm {g} _\infty}, we tentatively set \m {\l _{\Rm {DS}} =  N_{H,t} N_{H,r} / \g _{\Rm {DS}}} and \m {\l _{\Rm {Lasso}} =  1 / \g _{\Rm {Lasso}}}.
Still, there may be other values of \m {\g} (or \m {\l}) for which DS and Lasso are both better.

@@

In the following, we plot for different values and ratios of \m {N_B, N_{H,t}, N_{H,r}}.
We fix \m {N_R = \RB {3/2} N_B}.
%
\blank [big]
\externalfigure [error-small-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [error-small-more-wide-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 2, N_{H,t} = 8, N_{H,r} = 6}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [error-small-more-tall-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 8}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [error-medium-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [error-medium-more-wide-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [error-medium-more-tall-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [error-big-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 18}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [error-big-more-wide-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 6, N_{H,t} = 24, N_{H,r} = 18}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [error-big-more-tall-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 24}, with \m {6} stages, error.}

@@

In the following, we plot for \m {N_Y = N_R}, for different ratios of \m {N_{H,t}, N_{H,r}}.
%
\blank [big]
\externalfigure [error-medium-equal-square-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_R = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [error-medium-equal-wide-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_R = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [error-medium-equal-tall-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_R = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}

@@

In the following, we plot for \m {N_B = 4}, for different number of stages \m {3} and \m {9}.
We fix \m {N_R = \RB {3/2} N_B} with \m {6} stages again and in the below.
%
\blank [big]
\externalfigure [error-medium-more-square-three-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {3} stages, error.}
%
\blank [big]
\externalfigure [error-medium-more-wide-three-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {3} stages, error.}
%
\blank [big]
\externalfigure [error-medium-more-tall-three-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {3} stages, error.}
%
\blank [big]
\externalfigure [error-medium-more-square-nine-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {9} stages, error.}
%
\blank [big]
\externalfigure [error-medium-more-wide-nine-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {9} stages, error.}
%
\blank [big]
\externalfigure [error-medium-more-tall-three-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {9} stages, error.}

@@

In the following, we plot for different thresholds, for \m {N_B = 4}, focusing on each of OMP, Lasso, DS.
%
\blank [big]
\externalfigure [error-medium-more-square-six-oommpp.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
%
\blank [big]
\externalfigure [error-medium-more-wide-six-oommpp.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
%
\blank [big]
\externalfigure [error-medium-more-tall-six-oommpp.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of OMP, error.}
%
\blank [big]
\externalfigure [error-medium-more-square-six-lasso.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
%
\blank [big]
\externalfigure [error-medium-more-wide-six-lasso.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
%
\blank [big]
\externalfigure [error-medium-more-tall-six-lasso.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of Lasso, error.}
%
\blank [big]
\externalfigure [error-medium-more-square-six-ddss.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
%
\blank [big]
\externalfigure [error-medium-more-wide-six-ddss.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
%
\blank [big]
\externalfigure [error-medium-more-tall-six-ddss.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of DS, error.}

@@

When plotting runtime statistics, we only consider the cases where \m {N_{H,t} = N_{H,r} = 3 N_B}.
%
\blank [big]
\externalfigure [time-small-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [time-medium-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
%
\blank [big]
\externalfigure [time-big-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 18}, with \m {6} stages, error.}

### 2021-04-28 treatise-context/foreword.tex
pdflatex: Shrink figure width

\chapter* {Foreword}

@@

The present treatise is far from being remarkable, but I suppose the course of devising, clarifying, speculating, verifying, programming, debugging, googling, and polishing does teach some resilience to a weak mind.
The three and half years are punctuated by Bachi martial art practice session, TA preparation and scoring, chess club meeting, MediaTek internship, and the two semester courses of Real Analysis and Advanced Statistical Inference, which are recollections I hold dearly.

@@

>>>>

\starttitle [title={Foreword}]

@@

The present treatise is far from being remarkable, but I suppose the course of devising, clarifying, speculating, verifying, programming, debugging, googling, and polishing does teach some resilience to a weak mind.
The three and half years are punctuated by Bāchí martial art practice session, TA preparation and scoring, chess club meeting, MediaTek internship, and the two semester courses of Real Analysis and Advanced Statistical Inference, which are recollections I hold dearly.

@@

\stoptitle

### 2021-04-28 treatise-pdflatex/1_introduction.tex
pdflatex: Shrink figure width

It appears that, for a given number of sampling, DS recovers more successfully than OMP.
Moreover, our setting is more general than Alkhateeb, Leus, and Heath Jr.\ \cite {ALH15} with only an analog combiner,
and our random generation of sensing matrix is simpler than Lee, Gil, and Lee \cite {LGL16},
and we do not rely on additional assumptions on sparsity as in Gao, Dai, and Wang \cite {GDW15}.

@@

In addition, it seems that with the same threshold, DS is better than Lasso.
Again, our proposed method is more general than Lian, Liu and Lau \cite {LLL17} with only an analog combiner,
and our sensing matrix is generated more simply than in Destino, Juntti, and Nagaraj \cite {DJN15},
and we do not require special devices as in Vlachos, Alexandropoulos, and Thompson \cite {VAT19}.

>>>>

It appears that, for a given number of sampling, DS recovers better than OMP, except perhaps in high noise scenario.
Moreover, our setting is more general than Alkhateeb, Leus, and Heath Jr.\ \cite {ALH15} with only an analog combiner,
and our random generation of sensing matrix is simpler than Lee, Gil, and Lee \cite {LGL16},
and we do not rely on additional assumptions on sparsity as in Gao, Dai, and Wang \cite {GDW15}.

@@

In addition, it seems that with the same threshold, DS recovers better than Lasso, except perhaps in low noise scenario.
Again, our proposed method is more general than Lian, Liu and Lau \cite {LLL17} with only an analog combiner,
and our sensing matrix is generated more simply than in Destino, Juntti, and Nagaraj \cite {DJN15},
and we do not require special devices as in Vlachos, Alexandropoulos, and Thompson \cite {VAT19}.
Overall, it is clear that DS leads to a relatively better regularization than OMP and Lasso.

### 2021-04-28 treatise-pdflatex/3_2_generating_beamforming_matrices.tex
pdflatex: Shrink figure width

We argue as follows.
If angles \m {\th_l} (respectively \m {\f_l}) are exactly the multiples of \m {2 \pi / N_{H,t}} (respectively \m {2 \pi / N_{H,r}}), then
\DispNum {G:G:Ud:dU} {
\M {G}
=\M {U} \mathrm {diag} \SB {\V {d}'} \M {U} ^\dagger 
}
for some \m {S}-sparse \m {\V {d}'} and unitary \m {\M {U}}.
Clearly,
\DispNum {G:2:g2:g2} {
\VNm {\M {G}} _2
=\VNm {\mathrm {abs} \SB {\V {g}}} _2 
}
where \m {\mathrm {abs}} denotes entrywise absolute value.
Then if we notice that \m {\M {W} _B \M {W} _R \M {K} \M {U}} and \m {\M {U} ^\dagger \M {K}^\dagger \M {F} _R^\dagger \M {F} _B^\Adj} has \m {\d_s} RIP too, we see
\DispNum {W:2:WB:d's} {
&\VNm {\M {W} _B \M {W} _R \M {H} \M {F} _R \M {F} _B} _2 \notag \\
%
= &\VNm {
   \M {W} _B \M {W} _R \M {K} \M {U} \D
   \mathrm {diag} \SB {\mathrm {abs} \SB {\V {d}'}} \D
   \M {U} ^\dagger \M {K} ^\dagger \M {F} _R \M {F} _B} _2 \notag \\
%
= &\VNm {
   \M {W} _B \M {W} _R \M {K} \M {U}
   \R {\mathrm {abs} \SB {\V {d}'}} \D
   \R {\mathrm {abs} \SB {\V {d}'}}
   \M {U} ^\dagger \M {K} ^\dagger \M {F} _R \M {F} _B} _2 \notag \\
%
= &\VNm {
   \M {W} _B \M {W} _R \M {K} \M {U}
   \R {\mathrm {abs} \SB {\V {d}'}}} _2 \D
   \VNm {\M {F} _B ^\dagger \M {F} _R ^\dagger \M {K} \M {U}
   \R {\mathrm {abs} \SB {\V {d}'}}} _2 \notag \\
%
\eqsim &\VNm {\M {G}} _2 \RB {1 +2\d_s} 
}
Thus, even we cannot make sure that \m {\M {P}} is \m {\d_s} RIP with respect to all possible \m {\V {g}}'s, at least \m {\M {P}} has RIP with respect to relevant values of \m {\V {g}} according to the form \eqref {H:H:l0:ql}.

>>>>

We argue as follows.
If angles \m {\th_l} (respectively \m {\f_l}) are exactly the multiples of \m {2 \pi / N_{H,t}} (respectively \m {2 \pi / N_{H,r}}), then
\DispNum {G:G:Ud:dU} {
\M {G}
=\M {U} \mathrm {diag} \SB {\V {d}'} \M {U} ^\dagger 
}
for some \m {S}-sparse \m {\V {d}'} and unitary \m {\M {U}}.
Clearly,
\DispNum {G:2:g2:g2} {
\VNm {\M {G}} _2
=\VNm {\mathrm {abs} \SB {\V {g}}} _2 
}
where \m {\mathrm {abs}} denotes entrywise absolute value.
Then if we notice that \m {\M {W} _B \M {W} _R \M {K} _r \M {U}} and \m {\M {U} ^\dagger \M {K}^\dagger _t \M {F} _R^\dagger \M {F} _B^\Adj} has \m {\d_s} RIP too, we see
\DispNum {W:2:WB:d's} {
&\VNm {\M {W} _B \M {W} _R \M {H} \M {F} _R \M {F} _B} _2 \notag \\
%
= &\VNm {
   \M {W} _B \M {W} _R \M {K} _r \M {U} \D
   \mathrm {diag} \SB {\mathrm {abs} \SB {\V {d}'}} \D
   \M {U} ^\dagger \M {K} _t ^\dagger \M {F} _R \M {F} _B} _2 \notag \\
%
= &\VNm {
   \M {W} _B \M {W} _R \M {K} _r \M {U}
   \R {\mathrm {abs} \SB {\V {d}'}} \D
   \R {\mathrm {abs} \SB {\V {d}'}}
   \M {U} ^\dagger \M {K} _t ^\dagger \M {F} _R \M {F} _B} _2 \notag \\
%
= &\VNm {
   \M {W} _B \M {W} _R \M {K} _r \M {U}
   \R {\mathrm {abs} \SB {\V {d}'}}} _2 \D
   \VNm {\M {F} _B ^\dagger \M {F} _R ^\dagger \M {K} _t \M {U}
   \R {\mathrm {abs} \SB {\V {d}'}}} _2 \notag \\
%
\eqsim &\VNm {\M {G}} _2 \RB {1 +2\d_s} 
}
Thus, even we cannot make sure that \m {\M {P}} is \m {\d_s} RIP with respect to all possible \m {\V {g}}'s, at least \m {\M {P}} has RIP with respect to relevant values of \m {\V {g}} according to the form \eqref {H:H:l0:ql}.
